### 2018-06-02 Physics Notes/Paper 1/Paper 1.tex
Physics Notes Update

\begin{axis}[
    Stationary Wave,
    ticks=none,
    axis line style={draw=none}
]
\addplot [mark=none, ultra thick, blue] {sin(deg(x))};
\addplot [mark=none, ultra thick, red] {sin(deg(x+pi))};
\end{axis}
\end{tikzpicture}
\\
When both waves are at equilibrium there is a \textbf{node}\\
When one wave is at a maximum and one at a minimum there is an \textbf{antinode}\\
\\
\textbf{Stationary wave} - Wave pattern with nodes and antinodes formed when two or more progressive waves of the same frequency and amplitude pass through each other\\
\textbf{Node} - A fixed point in a stationary wave pattern where the amplitude is zero\\
\textbf{Antinode} - A fixed point in a stationary wave pattern where the amplitude is a maximum
\paragraph{Harmonics}
$$f_1=\frac{1}{2l}\sqrt{\frac{T}{\mu}}$$
T - String tension\\
$\mu$ - Mass/Length\\
\\
The formula for the nth harmonic is:
$$f_n=\frac{n}{2l}\sqrt{\frac{T}{\mu}}$$
\subsection{Refraction, diffraction and interference}
\subsubsection{Interference}
\textbf{Path difference} - The difference in distances from two coherent sources to an interference fringe\\
\textbf{Coherence} - Constant phase difference\\
\includegraphics[width=8cm]{Interference.jpg}
$$w=\frac{\lambda D}{s}$$
w- Separation of fringes (Distance between adjacent brightest points etc)\\
$\lambda$ - Wavelength\\
D - Distance from slits to screen\\
s - Separation of the two slits\\
\includegraphics[width=8cm]{Diffraction_Colours.png}
\subsubsection{Diffraction}
\includegraphics[width=7cm]{Diffraction.png}\\
Increasing the width of the slit causes the central maxima to get narrower, this can be remembered from the fringe spacing formula, remember the central maxima is double the width calculated using that formula though.
\paragraph{Diffraction grating equation}
\includegraphics[width=7cm]{nlambda_1.png}\\
\includegraphics[width=7cm]{nlambda_2.png}\\
Path difference =$d\sin\theta$\\
$n\lambda=d\sin\theta$\\
\\
A diffraction grating can be used to analyse spectra
\subsubsection{Refraction}
\textbf{Refractive index} - $\frac{\textrm{Speed of light in free space}}{\textrm{Speed of light in that medium}}$\\

>>>>

\begin{axis}[
    Stationary Wave,
    ticks=none,
    axis line style={draw=none}
\addplot [mark=none, ultra thick, blue] {sin(deg(x))};
\addplot [mark=none, ultra thick, red] {sin(deg(x+pi))};
\end{tikzpicture}
\\
When both waves are at equilibrium there is a \textbf{node}\\
When one wave is at a maximum and one at a minimum there is an \textbf{antinode}\\
\\
\textbf{Stationary wave} - Wave pattern with nodes and antinodes formed when two or more progressive waves of the same frequency and amplitude pass through each other\\
\textbf{Node} - A fixed point in a stationary wave pattern where the amplitude is zero\\
\textbf{Antinode} - A fixed point in a stationary wave pattern where the amplitude is a maximum
\paragraph{Harmonics}
$$f_1=\frac{1}{2l}\sqrt{\frac{T}{\mu}}$$
T - String tension\\
$\mu$ - Mass/Length\\
\\
The formula for the nth harmonic is:
$$f_n=\frac{n}{2l}\sqrt{\frac{T}{\mu}}$$
\subsection{Refraction, diffraction and interference}
\subsubsection{Interference}
\textbf{Path difference} - The difference in distances from two coherent sources to an interference fringe\\
\textbf{Coherence} - Constant phase difference\\
\includegraphics[width=8cm]{Interference.jpg}
$$w=\frac{\lambda D}{s}$$
w- Separation of fringes (Distance between adjacent brightest points etc)\\
$\lambda$ - Wavelength\\
D - Distance from slits to screen\\
s - Separation of the two slits\\
\includegraphics[width=8cm]{Diffraction_Colours.png}
\subsubsection{Diffraction}
\includegraphics[width=7cm]{Diffraction.png}\\
Increasing the width of the slit causes the central maxima to get narrower, this can be remembered from the fringe spacing formula, remember the central maxima is double the width calculated using that formula though.
\paragraph{Diffraction grating equation}
\includegraphics[width=7cm]{nlambda_1.png}\\
\includegraphics[width=7cm]{nlambda_2.png}\\
Path difference =$d\sin\theta$\\
$n\lambda=d\sin\theta$\\
\\
A diffraction grating can be used to analyse spectra
\subsubsection{Refraction}
\textbf{Refractive index} - $\frac{\textrm{Speed of light in free space}}{\textrm{Speed of light in that medium}}$
$$\textrm{Snell's law:} - n_1\sin\theta_1=n_2\sin\theta_2$$
$$\sin\theta_c=\frac{n_1}{n_2}$$
Total internal reflection occurs if the angle of incidence is \textbf{larger} than the critical value
\paragraph{Fibre optics}
\includegraphics[width=7cm]{Fibre_Optic_1.png}\\
\includegraphics[width=7cm]{Fibre_Optic_2.jpg}\\
\subsubsection{Modal Dispersion}
Waves entering the fibre at different angles will reflect differently and so will have different path lengths
\subsubsection{Material Dispersion}
Different wavelengths of light enter the same but refract differently, causing a difference in path length
\section{Mechanics and materials}
\subsection{Forces, energy and momentum}
\subsubsection{Moments}
\textbf{Moment} - Force $\times$ perpendicular distance from the line of action of the force to the point\\
\textbf{Couple} - A pair of equal and opposite coplanar forces
$$\textrm{Moment of a couple}=Fd$$
Where F is one of the forces, and d is the distance between them\\
\textbf{Principle of moments} - For an object in equilibrium, the sum of clockwise moments equals the sum of anticlockwise moments\\
\textbf{Centre of mass} - The point through which a single force on the body has no turning effect
\subsubsection{Projectile motion}
\paragraph{The effect of air resistance}
\includegraphics[scale=0.25]{Air_Resistance.JPG}\\
\textcolor{orange}{No Air Resistance}\\
\textcolor{red}{Air resistance
\item Steeper descent
\item Peak Further Left
\item Smaller Range
\end{itemize}}
\subsubsection{Newton's laws of motion}
\textbf{1st law} - An object remains at rest or in uniform motion unless acted on by a resultant force\\
\textbf{2nd law} - $F=ma$\\
\textbf{3rd law} - Every action has an equal and opposite reaction
\subsubsection{Momentum}
\textbf{Momentum} - Mass$\times$Velocity\\
\textbf{Impulse} - Change in momentum per second\\
\textbf{Elastic collision} - No loss of kinetic energy\\
\textbf{Inelastic collision} - Loss of kinetic energy
\subsubsection{Work, energy and power}
When \textbf{work} is done \textbf{energy} is transferred
$$W=FS\cos\theta$$
\subsubsection{Conservation of energy}
\textbf{Principle of conservation of energy} - Energy cannot be created or destroyed
\subsection{Materials}
\subsubsection{Bulk properties of solids}
\textbf{Hooke's law} - Force is proportional to extension, provided the proportionality limit has not been reached\\
\textbf{Breaking stress (Ultimate tensile stress)} - Tensile stress needed to break a solid material\\
\textbf{Plastic deformation} - Deformation of a solid beyond its elastic limit\\
\textbf{Brittle} - Snaps without bending or stretching when subject to stress\\
\textbf{Fracture} - The separation of a material into two or more pieces when subject to stress\\
\includegraphics[width=6cm]{metal.jpg}
\includegraphics[width=6cm]{rubber.jpg}
\includegraphics[width=6cm]{Stress_Strain.jpg}
\subsubsection{The Young Modulus}
\textbf{Young Modulus} - Stress/Strain assuming the limit of proportionality has not been reached
\section{Electricity}
\subsection{Current electricity}
\subsubsection{Basics of electricity}
\textbf{Current} - The rate of flow of charge\\
\textbf{Potential difference} - Work done per unit charge\\
\textbf{Resistance} - Voltage/current
\subsubsection{Current - Voltage characteristics}
\paragraph{Ohmic Conductor}
\begin{axis}[axis lines=middle, ticks=none,scale=0.5,    ylabel = Current,xlabel=Voltage,ylabel style={rotate=90}
\addplot[color=black]{x};
\end{tikzpicture}
\paragraph{Bulb}
\begin{axis}[axis lines=middle, ticks=none,scale=0.5,    ylabel = Current,xlabel=Voltage,ylabel style={rotate=90}
\addplot[color=black,domain=-90:90]{sin(x)};
\end{tikzpicture}
\paragraph{Diode}
\includegraphics[width=2in]{diode.jpeg}\\
\textbf{Ohm's Law}: Current is proportional to voltage under constant physical conditions
\subsubsection{Resistivity}
\paragraph{The effect of temperature on conductors}
The lower the temperature, the less the vibration of the atoms, and resistance reduces
\textbf{Superconductor} - A material that has no electrical resistance\\
\textbf{Critical temperature} - The temperature below which a conductor becomes a superconductor\\
\\
Superconductors are used for very high current applications.
\subsubsection{Circuits}
\paragraph{Resistor combinations}
$$\textrm{Series}: R_T=R_1+R_2+R_3...$$
$$\textrm{Parallel}: \frac{1}{R_T}=\frac{1}{R_1}+\frac{1}{R_2}+\frac{1}{R_3}+...$$
\paragraph{Voltage in series and parallel}
Parallel: Voltage across components in parallel is the same\\
Series: The total voltage across all the components is the voltage supplied
\paragraph{Current in series and parallel}
The current entering a component or junction is the same as the current leaving the component, meaning current in series is the same for each component.\\
For parallel circuits, use voltage and resistance to calculate
\paragraph{Power}
$$P=\frac{E}{t}$$
\paragraph{Kirchoff's laws}
Current in=Current out (Conservation of charge)\\
The sum of all the voltages around the system is zero (Conservation of energy)
\subsubsection{Potential divider}
$$V_{Out}=V_{In}\frac{R_2}{R_1+R_2}$$
Potential dividers can be used with environment sensors that change their resistance based on changed to the environment to change output voltage
\subsubsection{The electromotive force and internal resistance}
\textbf{Electromotive force} - The amount of electrical energy per unit charge produced inside a source of electrical energy\\
\textbf{Internal resistance} - Resistance inside a source of electrical energy\\
\textbf{Terminal pd} - The potential difference across the terminals of a power supply\\
\begin{axis}[axis lines=middle,scale=0.5,    ylabel = Vr,xlabel=Current,ylabel style={rotate=90,anchor=south},xlabel style={anchor=south},xmin=0,xmax=7,ymin=0,ymax=7,xtick={5},xticklabels={Short Circuit Current},ytick={5},yticklabels={$\epsilon$}
\addplot[color=black,domain=0:5]{-x+5};
\end{tikzpicture}
\\
The equation of this line can be derived from:
$$\epsilon=I(R+r)$$
Remember that the terminal voltage is $Ir$
